systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-15 paper/trunk/systemfit_other.tex
updated the hausman section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@592 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Hausman \citep{hausman78} developed a test have power against
alternatives for which $\hat{\theta}$ and $\tilde{\theta}$ diverge
under misspecification.
The resulting test statistic, distributed as a
$\chi^2$, is the difference between the covariance of an
efficient estimator and the covariance of the inefficient estimator.
If the difference is zero, the model is correctly specified.

@@

\begin{equation}
m = ( \beta_2 - \beta_3 )^{'} ( \Omega_2 - \Omega_3 ) ( \beta_2 - \beta_3 ) 
\label{eq:hausman}
\end{equation}
where $\beta_2$ and $\Omega_2$ are the estimated coefficients and the
variance-covariance matrix from a 2SLS estimation and $\beta_3$ and
$\Omega_3$ are the estimated coefficients and their variance
covariance-matrix from a 3SLS estimation.

>>>>

Hausman \citep{hausman78} developed a test have power against
alternatives for which $\hat{\beta}_2$ and $\hat{\beta}_3$ diverge
under misspecification.
The resulting test statistic, distributed as a
$\chi^2$, is the difference between the covariance of an
efficient estimator and the covariance of the inefficient estimator.
If the difference is zero, the model is correctly specified.

@@

\begin{equation}
  m = ( \hat{\beta}_2 - \hat{\beta}_3 )^{'} ( \hat{\Omega}_2 - \hat{\Omega}_3 ) ( \hat{\beta}_2 - \hat{\beta}_3 ) 
\label{eq:hausman}
\end{equation}
where $\hat{\beta}_2$ and $\hat{\Omega}_2$ are the estimated
coefficient and variance-covariance matrix from 2SLS estimation and
$\hat{\beta}_3$ and $\hat{\Omega}_3$ are the estimated coefficients
and variance covariance-matrix from 3SLS estimation.
